%        File: Sep11.latex
%     Created: Thu Sep 11 09:00 AM 2014 E
% Last Change: Thu Sep 11 09:00 AM 2014 E
%
\documentclass[a4paper,12pt]{article}
\begin{document}

\textbf{Sourabh Daptardar (108209783)   Sep 11, 2014 }

\section{Non-parametric Model for Background Subtraction}
\textbf{Authors:} Ahmed Elgammal, David Harwood, Larry Davis \\

\textbf{Method Summary:}
\begin{itemize}
    \item{\textbf{Basic Background Model:} Probability density function with a
        kernel $ Pr\left(x_t\right) = \frac{1}{n} \sum_{i=1}^{N} K\left(x_t -
    x_i\right) $ computed from recent sample of intensity values. $K$ is chosen
to be normal function. Thus, it is a non-parametric model and claimed to be
superior to mixture of $K$ gaussians}
    \item{\textbf{Suppress False Detections:} False Detections could be due to
    random noise which should be homogeneous or small movements which should be
spatially clustered. Assuming consecutive frames can have only small
displacements of pixels, detect if a pixel caused by movement of background
object in small neighborhood of the detection. Pixel displacement probability
and in turn connected component displacement probability are computed and
thresholds are set.}
    \item{\textbf{Shadow Detection:} $s = R + G + B$ is used as lightness
        measure. Set reasonable bounds on ratio of value of $s$ in a static background
    frame to that in the current frame }
    \item{\textbf{Background model updation:} Short term and long term models of
    background are computed an their intersection is taken.}
    \item{\textbf{Spatial Coherency:} Morphological operators.}
\end{itemize}

\textbf{Key Idea:} Non parametric model formulation.

\textbf{Advantage:} Overcomes limitations of Mixture of Gaussians model, like
low detection sensitivity or adaptations to targets.

\textbf{Disadvantage:} Too many parameters to tune.


\newpage
\section{Bayesian Modeling for Dynamic Scenes}
\textbf{Authors:} Yaser Sheikh, Mubarak Shah \\

\textbf{Method Summary:}

Unlike the previous paper, both the foreground objects and background are
modeled. The paper outlines three principles:
\begin{itemize}
    \item{\textbf{Spatial correlation:} Unlike the previous paper assumes that
    intensities of pixels are not independent but they correlated. So, this
paper represents background using a single function. This model is a function of
five variables : r, g, b, x and y. It uses Kernel Density Estimation technique
like the previous paper for the learning this model.}
    \item{\textbf{Temporal Persitence:} Interesting objects tend to remain in
    spatial vicinity and tend to maintain consistent colors from frame to frame.
Foreground objects are modeled as a mixture of uniform and Kernel function.}
    \item{\textbf{Spatial Context:} To remove the artifacts, generally
    morphological operators are used. This paper however, proposes Markov Random
Field formulation to remove the inconsistencies, making use of the fact that
objects in the real world tend to be spatially coherent. s-t cuts are used to
solve the optimization problem of MAP for the MRF.}
\end{itemize}

\textbf{Key Idea:} Modeling both foreground and background, and outlining three
new principles: spatial correlation, temporal persistence, spatial context.

\textbf{Advantage:} Principled approach.

\textbf{Disadvantage:} Complex as compared to previous approaches like Mixture
of Gaussians.

\end{document}


