%        File: Sep9.latex
%     Created: Tue Sep 09 08:00 AM 2014 E
% Last Change: Tue Sep 09 08:00 AM 2014 E
%
\documentclass[a4paper,12pt]{article}
\begin{document}
\textbf{Sourabh Daptardar (108209783)   Sep 9, 2014} \\
\section{Large Displacement Optical Flow: Descriptor Matching in Variational
Motion Estimation}
\textbf{Authors:} Thomas Bronx, Jitendra Malik

\textbf{Conference:} TPAMI 2010 \\

\textbf{Summary:}

This paper presents an approach of integrating descriptor matching into
variational framework for optical flow. Traditional variational model for
optical flow is formulated as the following energy functional minimization
problem:
\begin{equation}
    E(\mathbf{w}) = E_{color} + \gamma E_{gradient} + \alpha E_{smooth}
\end{equation}

The terms correspond to color constancy, gradient constancy and regularization
(smoothness) constraints. Solution is  by obtained by local minima corresponding to where
the first variants (derivatives) become zero. For initializing a coarse-to-fine
strategy is followed. Hence, solutions with larger structures are favoured due to
initializations. The result of this is that finer and faster motions are not
captured. On the other hand, feature descriptors can produce large number of
correct displacement correspondences. However, unlike variational model autorthey can
not produce dense motion fields. To get the best out of both worlds, two
descriptor based terms  are added to the variational formulation.
\begin{equation}
E(\mathbf{w}) = E_{color}(\mathbf{w}) + \gamma E_{gradient}(\mathbf{w}) + \alpha
E_{smooth}(\mathbf{w}) + \beta E_{match}(\mathbf{w,w_{1}}) + E_{desc}(\mathbf{w_{1}})
\end{equation} 

The function is non-convex, so we need good approximations. The paper shows how
the properties of descriptor matching and continuation method can be exploited
to simplify the optimization problem. \\

\textbf{Key Idea:}

Combining discrete descriptor matching into the variational framework. \\

\textbf{Positives:} Handles large displacements in optical flow. \\ 

\textbf{Limitations:} Non-convex formulation 

\newpage
\section{DeepFlow: large displacement optical flow with deep learning}

\textbf{Authors:} Philippe Weinzaepfel, Jerome Revaud, Zaid Harchoui, Cordelia Schmid

\textbf{Conference:} ICCV 2013

\textbf{Summary:}
This paper extends the idea of Bronx and Malik. They improve the descriptor
matching by adding dense correspondences matching and self smoothed matching.
They introduce a multi-stage architecture for descriptor matching with about six
layers, interleaving convolutions and max pooling. The construction has been
inspired by deep convolutional networks. This allows them to get denser
descriptor matches, as hierarchical model can provide for matches at coarser or
finer level. They also allow for warping of the descriptors and subdivide the
SIFT descriptor into smaller ($4 \times 4 $) patches and allowing flexibility in
the matches within appropriate limits. Thus non-rigid deformations can be
handled by this method. \\

\textbf{Key Idea:}

Convolutional net like structure and handling of non-rigid deformations. \\

\textbf{Advantages:}

Denser correspondences and non-rigid deformations \\

\textbf{Disadvantages:}

Complexity 

\end{document}


